MSDS6372Project1

### 2021-01-26 MSDS6372Project1.Rmd
update lasso coefficients

########################################
# Try LASSO variable selection #########
########################################
library(glmnet)
#Dummy code categorical predictor variables
x <- model.matrix(MSRP~.,train)[,-1]
y <- train$MSRP
set.seed(123) # Need a seed number to keep same results for LASSO
cv.out=cv.glmnet(x,y,alpha=1) #alpha=1 performs LASSO
par(mfrow=c(1,1))
plot(cv.out)
# Look at the coefficient for best lambda
coefficients = coef(cv.out, cv.out$lambda.min)
head(coefficients)
# Compute the final lasso model
lasso.model = glmnet(x,y,alpha = 1,lambda = cv.out$lambda.min)
# Check assumptions

>>>>

########################################
# Try LASSO variable selection #########
########################################
library(glmnet)
#Dummy code categorical predictor variables
x <- model.matrix(MSRP~.,train)[,-1]
y <- train$MSRP
set.seed(123) # Need a seed number to keep same results for LASSO
cv.out=cv.glmnet(x,y,alpha=1) #alpha=1 performs LASSO
par(mfrow=c(1,1))
plot(cv.out)
# Look at the coefficient for best lambda
# Make+Model+Year+EngineFuelType+EngineHP+EngineCylinders+TransmissionType+DrivenWheels+NumberOfDoors+VehicleSize+VehicleStyle+HighwayMPG+CityMPG+Popularity+Crossover+Diesel+Exotic+Luxury+HighPerformance+FactoryTurner+Performance+FlexFuel+Hatchback+Hybrid+Yes+N_A
# Lasso turned off some predictors in Make, Model,VehicleStyle... In order to check assumptions, we need to use lm model with all the predictors
# Although this won't imitate the Lasso model perfectly though.
coefficients = coef(cv.out, cv.out$lambda.min)
head(coefficients)
# Compute the final lasso model
lasso.model = glmnet(x,y,alpha = 1,lambda = cv.out$lambda.min)
# Check assumptions
